Delocalization of Eigenvectors in Random Matrices

### 2025-03-24 Draft.tex
Lemmas

\author{Georgi Ivanov\\Advisor: Dr. Kevin Yang}
\date{}
\doublespacing
\begin{document}
\renewcommand{\contentsname}{Contents}
\renewcommand{\refname}{References}

@@

$$\mathbb{E}\left\vert \mathcal{E}^{M, 1i}_t(z)_{ab}\right\vert^{2p}\leq C_p\mathbb{E}\left[ \mathcal{E}^{M, 1i}_t(z)_{ab} \right]^p$$

@@

\noindent With this we have all the necessary pieces to complete the estimation of all the QV terms $\mathcal{E}^{M, 1i}_t$, by changing the variable of integration w.r.t $\sigma = |\text{Im}w_s|$.
$$\left[\mathcal{E}_{t}^{M, 11}(z)_{ab}\right]\lesssim \int_0^{\tau_\sto\wedge t} \eta_s^{-1} W^{\delta_\sto}W^{-2}\eta_t^{-\frac{3}{2}}\max_{\alpha, \beta}|(\Theta_t S^{1/2})_{\alpha, \beta}|^2ds$$
$$\left[\mathcal{E}_{t}^{M, 11}(z)_{ab}\right]\lesssim W^{\delta_\sto}W^{-2}\eta_t^{-\frac{3}{2}} \max_{\alpha, \beta}|(\Theta_t S^{1/2})_{\alpha, \beta}|^2 \int_{\eta_t}^{\eta_0} \sigma^{-1}ds\lesssim W^{-4+\delta+\delta_\sto}\eta_t^{-\frac{5}{2}},$$
since $\max_{\alpha, \beta}|(\Theta_t S^{1/2})_{\alpha, \beta}|^2 \lesssim W^{-2}\eta_t^{-1}$ (\hyperref[lemma-a2]{Lemma A.2})and $\log \eta_t^{-1}\lesssim \log \eta^{-1}\lesssim W^{\delta}$ for any $\delta>0$. Similarly, the second and third terms are:

@@

\begin{equation*}=\max_{\alpha\beta}\int_0^{\tau_\sto\wedge}\sum_{x, x', u, v}S^{\frac{1}{2}}_{\alpha x}S^{\frac{1}{2}}_{\alpha x'}\overline{G_{x\beta}}G_{x'\beta}G_{xu}\overline{G_{x'u}}S_{uv}|G_{v\beta}|^2ds=\tag{6.2}\end{equation*}
\begin{equation*}=\max_{\alpha\beta}\int_0^{\tau_\sto\wedge}\sum_{x, x', u, v}\left(G^*S^{\frac{1}{2}, \alpha}GG^*S^{\frac{1}{2},\alpha}G\right)_{uu}S_{uv}|G_{v\beta}|^2ds\tag{6.2.1}\end{equation*}
By first applying the \hyperref[ward]{Ward identity} and then the operator norm bound $\|G\|_{op}\leq \eta_s^{-1}$, we have: 
$$\left(G^*S^{\frac{1}{2}, \alpha}GG^*S^{\frac{1}{2},\alpha}G\right)_{uu} = \eta_s^{-1}\left(G^*S^{\frac{1}{2}, \alpha}\text{Im}GS^{\frac{1}{2},\alpha}G\right)_{uu}\lesssim$$
$$\lesssim \eta_s^{-1}\left\|\sqrt{S^{\frac{1}{2}, \alpha}}\im G\sqrt{S^{\frac{1}{2}, \alpha}}\right\|_{\mathrm{op}}(G^*S^{\frac{1}{2}, \alpha}G)_{uu}\lesssim$$
\begin{equation*}\lesssim W^{-1}\eta_s^{-2}(G^*S^{\frac{1}{2}, \alpha}G)_{uu} = W^{-1}\eta_s^{-2}\sum_\gamma S^{\frac{1}{2}}_{\alpha\gamma}|G_{\gamma\beta}|^2\tag{6.2.2}\end{equation*}
Now, in both the display after $(6.2)$ and the one above we have terms of the form $S_{xy}|G_{yz}|^2$. To estimate this, we will use the a time $s\leq \tau_\sto$ before the stopping time, for which we know \cite{bandSDE}: $$|T_s(z)_{zy}|\lesssim |(\Theta_s)_{zy}|+|\E_s(z)_{xy}|\lesssim W^{-1}\eta_s^{-\frac{1}{2}}$$
$$\Rightarrow \sum_v S_{uv}|G_{v\beta}|^2\lesssim W^{\delta_\sto/10}S_{u\beta}+W^{\delta_\sto/10}\left[S^{1/2}T_s(z)S^{1/2}\right]_{u\beta}\lesssim$$ 
$$\lesssim W^{\delta_\sto}S_{u\beta} + W^{\delta_\sto/10}W^{-1}\eta_s^{-1/2}\lesssim W^{\delta_\sto/10}W^{-1}\eta_s^{-1/2},$$
since $\eta_s = O(1)$. This means that we can combine $(6.2.1)$ and $(6.2.2)$ along with the result above in order to integrate with a change of variable as before: \newpage
$$\left[\E_t^{M, 14}(z)_{ab}\right]\lesssim \int_0^{t\wedge \tau_\sto} W^{\delta_\sto/5}W^{-3}\eta_s^{-3}ds\lesssim$$
$$\lesssim W^{\delta_\sto/5}W^{-3}\int_{\eta_t}^{\eta_0}\sigma^{-3}d\sigma\lesssim W^{\delta_\sto/5}W^{-3}\eta_t^{-2}$$

By interpolating with the first bound we found, we get: 
$$\left[\E_t^{M, 14}(z)_{ab}\right] \lesssim \sqrt{ W^{\delta_\sto/10}W^{-4}\eta_t^{-4}}\sqrt{W^{\delta_\sto/5}W^{-3}\eta_t^{-2}}\lesssim W^{\frac{3\delta_\sto}{20}}W^{-\frac{7}{2}}\eta_t^{-3}$$

\subsubsection*{Result}
(3.14) \cite{bandSDE}. By Chebyshev inequality, we have that for any $\delta>0$ and $p\geq 1$, the following holds: 
$$\mathbb{P}\left(\left\vert \E_t^{M, 1j}(z)_{ab}\geq N^\delta [\E_t^{M, 1j}(z)_{ab}]^{1/2}\right\vert\right)\leq C_p N^{-2p\delta}$$

@@

In order to bound the squared term $\E_t^{S, \sto}(z)$, we will use \hyperref[cor-a3]{Corollary A.3} of \hyperref[lemma-a2]{Lemma A.2} (Display $(3.7)$ and Lemma 23 in \cite{bandSDE}, respectively) to state the following  bound: $$\sup_x \sum_y \{\text{Id}+(t-s)\Theta_t\}_{xy}+\sup_y \sum_x \{\text{Id}+(t-s)\Theta_t\}_{xy} = 1+O(\eta_t^{-1}\eta_s)$$
Then by Hölder's inequality and the bound above, we have: $$|\E_t^{S}(z)_{ab}|=\left\vert\int_0^{t\wedge \tau_\sto} \{\text{Id} + (t-s)\Theta_t\}\E_s^2(z) \{\text{Id} + (t-s)\Theta_t\}ds\right\vert \leq$$
$$\leq \int \left[1+O(\eta_t^{-1}\eta_s)\right]^2 \max_{a, b}|\E_s(z)_{ab}^2|ds \lesssim \int_0^{\tau_\sto \wedge t} \max_{a, b}|\E_s(z)_{ab}^2|ds + \int_0^{\tau_\sto \wedge t}\eta_t^{-2}\eta_s^{2} \max_{a, b}|\E_s(z)^2_{ab}|ds$$
We can bound $\max_{a, b}|\E_s(z)_{ab}^2|ds$ by using the definition of our stopping time. Since $s\leq \tau_\sto = \tau_{\sto, 1}\wedge \tau_{\sto, 2}$, by property of $\tau_{\sto, 1}$ and given a bound $N\leq W^{\frac{11}{8}-\nu}$ we have: $$\max_{a, b}|\E_s(z)_{ab}|<W^{\delta_\sto} W^{-\frac{3}{4}} \eta_s^{-1}\cdot W^{-1}\eta_s^{-\frac{1}{2}}$$
$$\max_{a, b}|\E_s(z)_{ab}|^2<W^{2\delta_\sto} W^{-\frac{3}{2}} \eta_s^{-2}\cdot W^{-2}\eta_s^{-1}=W^{2\delta_{\sto}} W^{-\frac{7}{2}}\eta_s^{-3} $$
Now, observe that by matrix multiplication, for any $a, b\in \Gamma$, we have: $$\E_s(z)^2_{ab} = \sum_{j=1}^N \E_s(z)_{aj}\E_s(z)_{jb}$$
$$\Rightarrow |\E_s(z)_{ab}^2|\leq \sum_{j=1}^N |\E_s(z)_{aj}||\E_s(z)_{jb}|\leq \sum_{j=1}^N \max_{x,y}|\E_s(z)_{xy}|^2 = N\max_{x,y}|\E_s(z)_{xy}|^2$$
$$\Rightarrow \max_{a,b}|\E_s(z)^2_{ab}|\leq W^{2\delta_\sto}W^{-\frac{28-11}{8}-\nu}\eta_s^{-2} = W^{2\delta_\sto}W^{-\frac{17}{8}-\nu}\eta_s^{-2}$$
Putting the last two results together gives us the following bound on $|\E_t^S(z)_{ab}|$:
$$|\E_t^S(z)_{ab}|\lesssim \int_0^t W^{2\delta_\sto}W^{-\frac{17}{8}-\nu}\eta_s^{-2}ds + \int_0^t \eta_t^{-2}W^{2\delta_\sto}W^{-\frac{17}{8}-\nu}\eta_s^{-1}ds$$
By doing a change of variable for $\sigma = \im w_s$, we get: 
\begin{equation*}
|\E_t^{S, \sto}(z)_{ab}|\lesssim W^{2\delta_\sto} W^{-\frac{17}{8}-\nu}\int_{\eta_t}^{\im w_0}\sigma^{-3}d\sigma + \eta_t^{-2} W^{2\delta_\sto} W^{-\frac{17}{8}-\nu}\int_{\eta_t}^{\im w_0}\sigma^{-1}d\sigma
\end{equation*}
\begin{equation*}
\lesssim W^{2\delta_\sto} W^{-\frac{17}{8}-\nu} \left(\frac{\im w_0^{-2}-\eta_t^{-2}}{-2}\right)+W^{2\delta_\sto}W^{-\frac{17}{8}-\nu}\eta_t^{-2}\left(\log \im w_0-\log \eta_t\right)
\end{equation*}
By \hyperref[lemma-a12]{Lemma A.1.2} for any $s\in [0, t]$, we have $\im w_s = \im w_t+(t-s)\im m(z)\geq \im w_t$
and \hyperref[2.1]{$\im m(z)\asymp 1$}:
$$\Rightarrow \im w_s = \eta+(1-s)\im m(z)\leq \eta+ \im m(z) = \im w_0 = \frac{\im m(z)}{|m(z)|^2}\leq \im m(z)\lesssim 1\Leftrightarrow \log \im w_0\lesssim 0$$
Hence, we can drop the negative term w.r.t. $\im w_0^{-2}$ and bound above by $\log \im w_0\lesssim 0$:
\begin{equation*}
|\E_t^{S, \sto}(z)_{ab}|\lesssim W^{2\delta_\sto} W^{-\frac{17}{8}-\nu} \eta_t^{-2}+W^{2\delta_\sto}W^{-\frac{17}{8}-\nu}\eta_t^{-2}\log \eta_t^{-1} \lesssim W^{2\delta_\sto}W^{-\frac{17}{8}-\nu}\eta_t^{-2}\log \eta_t^{-1}
\end{equation*}
Observe that the latter expression can be split in the following terms: $$|\E_t^{S, \sto}(z)_{ab}|\lesssim W^{2\delta_\sto} W^{-\frac{3}{8}-\nu} \eta_t^{-\frac{1}{2}}\log \eta_t^{-1}\cdot W^{-\frac{3}{4}}\eta_t^{-1}\cdot W^{-1}\eta_t^{-\frac{1}{2}}$$
In this context, since $\eta_t \geq \eta\geq W^{-3/4}$, the first term is: $$W^{2\delta_\sto} W^{-\frac{3}{8}-\eta}\eta_t^{-\frac{1}{2}}\log \eta_t^{-1}\lesssim W^{2\delta_\sto-\nu}\log W,$$
But since $\eta>0$ is fixed, we can pick $\delta_\sto$ small, s.t. the latter term is $\lesssim 1$, meaning that our result above can be stated as: 
\begin{boxtheorem}{Theorem 6.3. }There $\exists \delta>0$, s.t.:
$$|\E_t^{S, \sto}(z)_{ab}|\lesssim W^{-\delta}\cdot W^{-\frac{3}{4}}\eta_t^{-1}\cdot W^{-1}\eta_t^{-\frac{1}{2}}$$
\end{boxtheorem}

@@

\subsection{Theorem 1 - Stopping time}
\label{proof-stop}

\subsection{Theorem 2 - Quantum Diffusion}

\subsection{Theorem 3 - Delocalization}
\label{proof-deloc}

@@

\begin{boxt}{Lemma A.1.1} \label{lemma-a11} $$ 1-|m|^2 \asymp \eta$$ 
\end{boxt}
\textit{Proof} Proofs can be found in Lemma 3.5 \cite{21} and Lemma 6.2 \cite{dynamic}).

\begin{boxt}{Lemma A.1.2} \label{lemma-a12} 
\begin{itemize}
\item $ \im w_s = \im w_t + (t-s)\im m(z)$ 
\item $(t-s)\lesssim \eta_s $
\end{itemize}

\end{boxt}
\textit{Proof}- Recall the definition $w_s = -\frac{1}{m(z)} - sm(z)$, where $m(z)$ is the stieltjes transform. By taking its imaginary part, we have: $$\im w_s = -\im \left( \frac{1}{m(z)}\right)-s\im m(z)= -\im \left( \frac{1}{m(z)}\right)-t\im m(z) + (t-s)\im m(z)$$
$$=\im w_t + (t-s)\im m(z)$$
Since $|\im m(z)|$ is bounded uniformly away from $0$ in the bulk (Lemma 6.2. in \cite{dynamic}) - \textcolor{red}{deduce} that $(t-s)\lesssim \eta_s $

\begin{boxt}{Lemma A.2} \label{lemma-a2} -
 For $|E|<2$ fixed and $\eta\gtrsim W^2/N^2$, then $$(\Theta_t)_{ab} + |(\Theta_tS^{\frac{1}{2}})_{ab}| + |\left(S^{\frac{1}{2}}\Theta_t S^{\frac{1}{2}}\right)_{ab}|\lesssim W^{-1}\eta_t^{-\frac{1}{2}}, $$
 $$\max_a \sum_b |(\Theta_t)_{ab}|+\max_a \sum_b |(\Theta_tS^{\frac{1}{2}})_{ab}|\lesssim \eta_t^{-1}$$
\end{boxt}
Proof can be found as Lemma 23 in \cite{bandSDE}. From the latter result it clearly follows that $\max_{a,b}\Theta_{ab} \lesssim W^{-1}\eta^{-1/2}$.

\begin{boxt}{Corollary A.3} \label{cor-a3} -
$$\sup_x \sum_y \{\text{Id}+(t-s)\Theta_t\}_{xy} + \sup_y \sum_x \{\text{Id} + (t-s)\Theta_t\}_{xy} = 1+O(\eta_t^{-1}\eta_s)$$
 \end{boxt}
 \textit{Proof} - Can be found as expression $(3.7)$ in \cite{bandSDE}.

\begin{boxt}{Lemma A.4} \label{lemma-a4} -) $\sum_y |B_{xy}|$ and $\sum_y |S_{xy}|$ have size $O(1)$. )

 Lemma 25 \cite{bandSDE} - For $|E|<2$ fixed and arbitrary $a, b$, we have: $$\sum_\alpha |(B_t)_{\alpha b}| + \sum_{\beta}|(B_t)_{a\beta}|\lesssim 1$$
 \end{boxt}

@@

\begin{boxt}{Lemma B.1} \label{lemma-b1}

$$\sup_x \sum_y |G_{xy}|\lesssim W^{\frac{\delta_\sto}{20}}W^{\frac{1}{2}+\epsilon} \eta_s^{-\frac{3}{4}}$$
\end{boxt}
\textit{Proof} - (Result $4.5$ \cite{bandSDE})

\begin{boxt}{Lemma B.2} \label{lemma-b2}

$$\max_{x, y} |G_{xy} - \delta_{xy}m(z)|\lesssim W^{\frac{\delta_\sto}{20}}W^{-\frac{1}{2}} \eta_s^{-\frac{1}{4}}
$$
\end{boxt}
\textit{Proof} - (Result $4.6$ \cite{bandSDE})

\subsubsection*{Off-diagonal $G_{xy}$ estimate}

\subsection*{Diagonal $|G_{xx}-m(z)|$ estimate}

>>>>

\author{Georgi Ivanov\\Advisor: Dr. Kevin Yang}
\date{}
\doublespacing
\begin{document}
\renewcommand{\refname}{References}
\renewcommand{\contentsname}{Contents}

@@

\begin{equation*}\mathbb{E}\left\vert \mathcal{E}^{M, 1i}_t(z)_{ab}\right\vert^{2p}\leq C_p\mathbb{E}\left[ \mathcal{E}^{M, 1i}_t(z)_{ab} \right]^p\tag{6.3}\end{equation*}

@@

\noindent With this we have all the necessary pieces to complete the estimation of all the QV terms $\mathcal{E}^{M, 1i}_t$, by changing the variable of integration w.r.t $\sigma = |\text{Im}w_s|$. As such, for any $\delta>0$:
$$\left[\mathcal{E}_{t}^{M, 11}(z)_{ab}\right]\lesssim \int_0^{\tau_\sto\wedge t} \eta_s^{-1} W^{\delta_\sto}W^{-2}\eta_t^{-\frac{3}{2}}\max_{\alpha, \beta}|(\Theta_t S^{1/2})_{\alpha, \beta}|^2ds$$
$$\left[\mathcal{E}_{t}^{M, 11}(z)_{ab}\right]\lesssim W^{\delta_\sto}W^{-2}\eta_t^{-\frac{3}{2}} \max_{\alpha, \beta}|(\Theta_t S^{1/2})_{\alpha, \beta}|^2 \int_{\eta_t}^{\eta_0} \sigma^{-1}ds\lesssim W^{-4+\delta+\delta_\sto}\eta_t^{-\frac{5}{2}},$$
since $\max_{\alpha, \beta}|(\Theta_t S^{1/2})_{\alpha, \beta}|^2 \lesssim W^{-2}\eta_t^{-1}$ (\hyperref[lemma-a2]{Lemma A.2}) and $\log \eta_t^{-1}\lesssim \log \eta^{-1}\lesssim W^{\delta}$. Similarly, the second and third terms are:

@@

\begin{equation*}=\max_{\alpha\beta}\int_0^{\tau_\sto\wedge}\sum_{x, x', u, v}S^{\frac{1}{2}}_{\alpha x}S^{\frac{1}{2}}_{\alpha x'}\overline{G_{x\beta}}G_{x'\beta}G_{xu}\overline{G_{x'u}}S_{uv}|G_{v\beta}|^2ds=\tag{6.4}\end{equation*}
\begin{equation*}=\max_{\alpha\beta}\int_0^{\tau_\sto\wedge}\sum_{x, x', u, v}\left(G^*S^{\frac{1}{2}, \alpha}GG^*S^{\frac{1}{2},\alpha}G\right)_{uu}S_{uv}|G_{v\beta}|^2ds\tag{6.4.1}\end{equation*}
By first applying the \hyperref[ward]{Ward identity} and then the operator norm bound $\|G\|_{op}\leq \eta_s^{-1}$, we have: 
$$\left(G^*S^{\frac{1}{2}, \alpha}GG^*S^{\frac{1}{2},\alpha}G\right)_{uu} = \eta_s^{-1}\left(G^*S^{\frac{1}{2}, \alpha}\text{Im}GS^{\frac{1}{2},\alpha}G\right)_{uu}\lesssim$$
$$\lesssim \eta_s^{-1}\left\|\sqrt{S^{\frac{1}{2}, \alpha}}\im G\sqrt{S^{\frac{1}{2}, \alpha}}\right\|_{\mathrm{op}}(G^*S^{\frac{1}{2}, \alpha}G)_{uu}\lesssim$$
\begin{equation*}\lesssim W^{-1}\eta_s^{-2}(G^*S^{\frac{1}{2}, \alpha}G)_{uu} = W^{-1}\eta_s^{-2}\sum_\gamma S^{\frac{1}{2}}_{\alpha\gamma}|G_{\gamma\beta}|^2\tag{6.4.2}\end{equation*}
Now, in both the display after $(6.4)$ and the one above we have terms of the form $S_{xy}|G_{yz}|^2$. To estimate this, we will use the a time $s\leq \tau_\sto$ before the stopping time, for which we know \cite{bandSDE}: $$|T_s(z)_{zy}|\lesssim |(\Theta_s)_{zy}|+|\E_s(z)_{xy}|\lesssim W^{-1}\eta_s^{-\frac{1}{2}}$$
$$\Rightarrow \sum_v S_{uv}|G_{v\beta}|^2\lesssim W^{\delta_\sto/10}S_{u\beta}+W^{\delta_\sto/10}\left[S^{1/2}T_s(z)S^{1/2}\right]_{u\beta}\lesssim$$ 
$$\lesssim W^{\delta_\sto}S_{u\beta} + W^{\delta_\sto/10}W^{-1}\eta_s^{-1/2}\lesssim W^{\delta_\sto/10}W^{-1}\eta_s^{-1/2},$$
since $\eta_s = O(1)$. This means that we can combine $(6.4.1)$ and $(6.4.2)$ along with the result above in order to integrate with a change of variable as before: \newpage
$$\left[\E_t^{M, 14}(z)_{ab}\right]\lesssim \int_0^{t\wedge \tau_\sto} W^{\delta_\sto/5}W^{-3}\eta_s^{-3}ds\lesssim$$
$$\lesssim W^{\delta_\sto/5}W^{-3}\int_{\eta_t}^{\eta_0}\sigma^{-3}d\sigma\lesssim W^{\delta_\sto/5}W^{-3}\eta_t^{-2}$$

\noindent By interpolating with the first bound we found, we get: 
$$\left[\E_t^{M, 14}(z)_{ab}\right] \lesssim \sqrt{ W^{\delta_\sto/10}W^{-4}\eta_t^{-4}}\sqrt{W^{\delta_\sto/5}W^{-3}\eta_t^{-2}}\lesssim W^{\frac{3\delta_\sto}{20}}W^{-\frac{7}{2}}\eta_t^{-3}\lesssim W^{\frac{\delta_\sto}{5}}W^{-\frac{7}{2}}\eta_t^{-3}$$
As such, we have in fact showed that for all $i=1, \cdots 4$ $$[\E_t^{M, 1j}(z)_{ab}]\lesssim W^{\frac{\delta_\sto}{5}}\lesssim W^{\delta_\sto/5}W^{-\frac{3}{2}}\eta_t^{-2}W^{-2}\eta_t^{-1}$$
By applying Chebyshev to the BDG inequality $(6.3)$, we have that for any $\delta>0$ and $p\geq 1$: 
\begin{equation*}\mathbb{P}\left(\left\vert \E_t^{M, 1j}(z)_{ab}\right\vert\geq N^\delta [\E_t^{M, 1j}(z)_{ab}]^{1/2}\right)\leq C_p N^{-2p\delta}\tag{6.5}\end{equation*}
Using Boole's inequality and a "standard Hölder continuity argument"  are sufficient to show \cite{bandSDE}:
$$\frac{\left\vert \E_t^{M_1, j}(z)_{ab}\right\vert}{W^{-\frac{3}{4}}\eta_t^{-1}W^{-1}\eta_t^{-\frac{1}{2}}}\prec W^{\frac{\delta_\sto}{5}}$$

@@

Recall \hyperref[cor-a3]{Corollary A.3} of \hyperref[lemma-a2]{Lemma A.2}: $$\sup_x \sum_y \{\text{Id}+(t-s)\Theta_t\}_{xy}+\sup_y \sum_x \{\text{Id}+(t-s)\Theta_t\}_{xy} = 1+O(\eta_t^{-1}\eta_s)$$
Then by Hölder's inequality and the bound above, we have: $$|\E_t^{S}(z)_{ab}|=\left\vert\int_0^{t\wedge \tau_\sto} \{\text{Id} + (t-s)\Theta_t\}\E_s^2(z) \{\text{Id} + (t-s)\Theta_t\}ds\right\vert \leq$$
$$\leq \int \left[1+O(\eta_t^{-1}\eta_s)\right]^2 \max_{a, b}|\E_s(z)_{ab}^2|ds \lesssim \int_0^{\tau_\sto \wedge t} \max_{a, b}|\E_s(z)_{ab}^2|ds + \int_0^{\tau_\sto \wedge t}\eta_t^{-2}\eta_s^{2} \max_{a, b}|\E_s(z)^2_{ab}|ds$$
We can bound $\max_{a, b}|\E_s(z)_{ab}^2|ds$ by using the definition of our stopping time. Since $s\leq \tau_\sto = \tau_{\sto, 1}\wedge \tau_{\sto, 2}$, by property of $\tau_{\sto, 1}$ and given a bound $N\leq W^{\frac{11}{8}-\nu}$ we have: $$\max_{a, b}|\E_s(z)_{ab}|<W^{\delta_\sto} W^{-\frac{3}{4}} \eta_s^{-1}\cdot W^{-1}\eta_s^{-\frac{1}{2}}$$
$$\max_{a, b}|\E_s(z)_{ab}|^2<W^{2\delta_\sto} W^{-\frac{3}{2}} \eta_s^{-2}\cdot W^{-2}\eta_s^{-1}=W^{2\delta_{\sto}} W^{-\frac{7}{2}}\eta_s^{-3} $$
Now, observe that by matrix multiplication, for any $a, b\in \Gamma$,$\E_s(z)^2_{ab} = \sum_{j=1}^N \E_s(z)_{aj}\E_s(z)_{jb}$:
$$\Rightarrow |\E_s(z)_{ab}^2|\leq \sum_{j=1}^N |\E_s(z)_{aj}||\E_s(z)_{jb}|\leq \sum_{j=1}^N \max_{x,y}|\E_s(z)_{xy}|^2 = N\max_{x,y}|\E_s(z)_{xy}|^2$$
$$\Rightarrow \max_{a,b}|\E_s(z)^2_{ab}|\leq W^{2\delta_\sto}W^{-\frac{28-11}{8}-\nu}\eta_s^{-2} = W^{2\delta_\sto}W^{-\frac{17}{8}-\nu}\eta_s^{-2}$$
Putting the last two results together gives us the following bound on $|\E_t^{S, \mathrm{stop}}(z)_{ab}|$:
$$|\E_t^{S, \mathrm{stop}}(z)_{ab}|\lesssim \int_0^t W^{2\delta_\sto}W^{-\frac{17}{8}-\nu}\eta_s^{-2}ds + \int_0^t \eta_t^{-2}W^{2\delta_\sto}W^{-\frac{17}{8}-\nu}\eta_s^{-1}ds$$
\begin{equation*}
|\E_t^{S, \sto}(z)_{ab}|\lesssim W^{2\delta_\sto} W^{-\frac{17}{8}-\nu}\int_{\eta_t}^{\im w_0}\sigma^{-3}d\sigma + \eta_t^{-2} W^{2\delta_\sto} W^{-\frac{17}{8}-\nu}\int_{\eta_t}^{\im w_0}\sigma^{-1}d\sigma
\end{equation*}
\begin{equation*}
\lesssim W^{2\delta_\sto} W^{-\frac{17}{8}-\nu} \left(\frac{\im w_0^{-2}-\eta_t^{-2}}{-2}\right)+W^{2\delta_\sto}W^{-\frac{17}{8}-\nu}\eta_t^{-2}\left(\ln \im w_0-\ln \eta_t\right)
\end{equation*}
By \hyperref[lemma-a12]{Lemma A.1.2} for any $s\in [0, t]$, we have $\im w_s = \im w_t+(t-s)\im m(z)\geq \im w_t$
and \hyperref[2.1]{$\im m(z)\asymp 1$}, which imply $\eta\leq \im w_s\lesssim 1$. And since $|\log \eta|\prec 1$ (follows by $\eta\geq W^{-3/4}$), we have that $|\log \im w_s|\prec 1$. Hence, we can drop the negative term w.r.t. $\im w_0^{-2}$ and bound above :
\begin{equation*}
|\E_t^{S, \sto}(z)_{ab}|\lesssim W^{2\delta_\sto} W^{-\frac{17}{8}-\nu} \eta_t^{-2}+W^{2\delta_\sto}W^{-\frac{17}{8}-\nu}\eta_t^{-2}\log \eta_t^{-1} \lesssim W^{2\delta_\sto}W^{-\frac{17}{8}-\nu}\eta_t^{-2}\log \eta_t^{-1}
\end{equation*}
Observe that the latter expression can be split in the following terms: $$|\E_t^{S, \sto}(z)_{ab}|\lesssim W^{2\delta_\sto} W^{-\frac{3}{8}-\nu} \eta_t^{-\frac{1}{2}}\log \eta_t^{-1}\cdot W^{-\frac{3}{4}}\eta_t^{-1}\cdot W^{-1}\eta_t^{-\frac{1}{2}}$$
In this context, since $\eta_t \geq \eta\geq W^{-3/4}$, the first term is: $$W^{2\delta_\sto} W^{-\frac{3}{8}-\eta}\eta_t^{-\frac{1}{2}}\log \eta_t^{-1}\lesssim W^{2\delta_\sto-\nu}\log W,$$
But since $\eta>0$ is fixed, we can pick $\delta_\sto$ small, s.t. the latter term is $\lesssim 1$, meaning that our result above can be stated as: 
\begin{boxtheorem}{Theorem 6.3. }There $\exists \delta>0$, s.t.:
$$|\E_t^{S, \sto}(z)_{ab}|\lesssim W^{-\delta}\cdot W^{-\frac{3}{4}}\eta_t^{-1}\cdot W^{-1}\eta_t^{-\frac{1}{2}}$$
\end{boxtheorem}

@@

\subsection*{7.1 Theorem 1 - Stopping time}
\label{proof-stop}

\begin{boxtheorem}{Theorem 1: (Stopping time).} $\mathbb{P}[\tau_{\text{stop}, i} \neq  1] \lesssim_D N^{-D}$ for any $i=1, 2$ and $D > 0$.
\end{boxtheorem}
\textit{Proof} - By Boole's inequality

\subsection*{7.2 Theorem 2 - Quantum Diffusion}
\begin{boxtheorem}{Theorem 2: (Quantum Diffusion)}
For $|E|<2$ fixed, assume $\exists \nu>0$, s.t. $\eta \asymp W^2 N^{-2}$ and $W\geq W^{8/11+\nu}$. Then: $$\max_{x, y}|T_{xy}-\Theta_{xy}|\prec W^{-\frac{7}{4}}\eta^{-\frac{3}{2}}$$
\end{boxtheorem}
\textit{Proof} -

\subsection*{7.3 Theorem 3 - Delocalization}
\label{proof-deloc}
\begin{boxtheorem}{Theorem 3}
\noindent Assume $|E|<2$ is fixed and that $\exists \nu>0$, s.t. $\eta \asymp W^2 N^{-2}$ and $W\geq N^{8/11+\nu}$. Then:
\begin{center}$\max_{x, y}|G_{xy} - \delta_{xy}m(z)|^2\prec W^{-1}\eta^{-\frac{1}{2}}$\end{center}
\end{boxtheorem}
\textit{Proof} -

@@

\begin{boxt}{Lemma A.1.1} \label{lemma-a11} $$ 1-|m|^2 \asymp \eta$$ 
\end{boxt}
\textit{Proof} - can be found in Lemma 3.5 \cite{21} and Lemma 6.2 \cite{dynamic}).

\begin{boxt}{Lemma A.1.2} \label{lemma-a12} 
\begin{enumerate}
\item $ \im w_s = \im w_t + (t-s)\im m(z)$ 
\item $(t-s)\lesssim \eta_s $
\end{enumerate}

\end{boxt}
\textit{Proof}- Recall the definition $w_s = -\frac{1}{m(z)} - sm(z)$, where $m(z)$ is the stieltjes transform. By taking its imaginary part, we have: $$\im w_s = -\im \left( \frac{1}{m(z)}\right)-s\im m(z)= -\im \left( \frac{1}{m(z)}\right)-t\im m(z) + (t-s)\im m(z)$$
$$=\im w_t + (t-s)\im m(z),$$
which proves the first identity. Rearrange as: 
$$\im w_s\geq \im w_s\im w_t= (t-s)\im m(z)$$
Since $|\im m(z)|$ is bounded uniformly away from $0$ in the bulk (Lemma 6.2. in \cite{dynamic} and $\im w_t\geq 0$ by def. , we can take the absolute value divide by $\im m(z)$ the result above, s.t. we get $(t-s)\lesssim \eta_s$.

\begin{boxt}{Lemma A.2} \label{lemma-a2} -
 For $|E|<2$ fixed and $\eta\gtrsim W^2/N^2$, then $$(\Theta_t)_{ab} + |(\Theta_tS^{\frac{1}{2}})_{ab}| + |\left(S^{\frac{1}{2}}\Theta_t S^{\frac{1}{2}}\right)_{ab}|\lesssim W^{-1}\eta_t^{-\frac{1}{2}}, $$
 $$\max_a \sum_b |(\Theta_t)_{ab}|+\max_a \sum_b |(\Theta_tS^{\frac{1}{2}})_{ab}|\lesssim \eta_t^{-1}$$
\end{boxt}
Proof can be found as Lemma 23 in \cite{bandSDE}. From it clearly follows that $\max_{a,b}\Theta_{ab} \lesssim W^{-1}\eta^{-1/2}$.

\begin{boxt}{Corollary A.3} \label{cor-a3} 
$$\sup_x \sum_y \{\text{Id}+(t-s)\Theta_t\}_{xy} + \sup_y \sum_x \{\text{Id} + (t-s)\Theta_t\}_{xy} = 1+O(\eta_t^{-1}\eta_s)$$
 \end{boxt}
 \textit{Proof} - Can be found as expression $(3.7)$ in the proof of Lemma 9 \cite{bandSDE}.

\begin{boxt}{Lemma A.4} \label{lemma-a4} - For $|E|<2$ fixed and arbitrary $a, b$, we have for $B_t  =(\text{Id} - tm(z)^2S)^{-1}$: $$\sum_\alpha |(B_t)_{\alpha b}| + \sum_{\beta}|(B_t)_{a\beta}|\lesssim 1$$
 \end{boxt}
 \textit{Proof} - found as Lemma 25 in \cite{bandSDE}. Clearly it implies that $\sum_y |B_{xy}|$ and $\sum_y |S_{xy}|$ are $\lesssim 1$.

@@

\begin{boxtheorem}{Lemma B.1} \label{lemma-b1}

$$\sup_x \sum_y |G_{xy}|\lesssim W^{\frac{\delta_\sto}{20}}W^{\frac{1}{2}+\epsilon} \eta_s^{-\frac{3}{4}}$$
\end{boxtheorem}
\textit{Proof} - can be found as result $4.5$ in \cite{bandSDE}.

\begin{boxtheorem}{Lemma B.2} \label{lemma-b2}

$$\max_{x, y} |G_{xy} - \delta_{xy}m(z)|\lesssim W^{\frac{\delta_\sto}{20}}W^{-\frac{1}{2}} \eta_s^{-\frac{1}{4}}
$$
\end{boxtheorem}
\textit{Proof} - can be found as result $4.6$ in \cite{bandSDE}).

\begin{boxtheorem}{Lemma B.3 (Off-diagonal $G_{xy}$)} \label{lemma-b3} - Let $\max_x|G_t(z)_{xx}|\prec 1$ and $\max_{x\neq y}|G_t(z)_{xy}|\prec W^{-\delta}$ for some $\delta>0$. Then, for any fixed $t\in [0, 1]$:$$\max_{a\neq b} \frac{|G_t(z)_{ab}|^2}{(S^{1/2}T_t(z)S^{1/2})_{ab}+S_{ab}^{1/2}}\prec 1$$
